On the properties of discs around accreting brown dwarfs

### 2010-06-30 BDD_submit/paper.tex
demonstrate misspelt in abstract
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2321 25464f21-6099-402c-b30a-640f1d40d38b
Problems with Figure 7 caption rectified
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2332 25464f21-6099-402c-b30a-640f1d40d38b

  We present a grid of models of accreting brown dwarf systems with
  circumstellar discs. The calculations involve a self-consistent
  solution of both vertical hydrostatic and radiative equilibrium
  along with a sophisticated treatment of dust sublimation. We have
  simulated observations of the spectral energy distributions and
  several broadband photometric systems. Analysis of the disc
  structures and simulated observations reveal a natural dichotomy in
  accretion rates, with \logmdot $>-$9 and $\leq -$9 classed as
  extreme and typical accretors respectively.  Derivation of ages and
  masses from our simulated photometry using isochrones is demostrated
  to be unreliable even for typical accretors. Although current brown
  dwarf disc candidate selection criteria have been shown to be
  largely reliable when applied to our model grid we suggest improved
  selection criteria in several colour indices. We show that as
  accretion rates increase brown dwarf disc systems are less likely to
  be correctly identified. This suggests that, within our grid,
  systems with higher accretion rates would be preferentially lost
  during brown dwarf target selection. We suggest that observations
  used to assert a $\dot{M}\propto M_*^2$ relationship may contain an
  intrinsic selection bias.

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.ps}
  \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
    inclination, shown as top, middle and lower panels
    respectively. The magnitudes of systems with $M_*=0.04M_{\odot}$,
    an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
    days are shown as crosses. The systems with accretion rates of
    \logmdot = $-$12, $-$9 and $-$7, are shown in black, red and blue
    respectively. The panels also the systems with the highest
    accretion rate but for a rotation rate of 5 days. The lowest panel
    also shows, as horizontal dotted lines, the total change of colour
    with the illustrated inclinations. \label{flare_mag}}
\end{figure*}

>>>>

  We present a grid of models of accreting brown dwarf systems with
  circumstellar discs. The calculations involve a self-consistent
  solution of both vertical hydrostatic and radiative equilibrium
  along with a sophisticated treatment of dust sublimation. We have
  simulated observations of the spectral energy distributions and
  several broadband photometric systems. Analysis of the disc
  structures and simulated observations reveal a natural dichotomy in
  accretion rates, with \logmdot $>-$9 and $\leq -$9 classed as
  extreme and typical accretors respectively.  Derivation of ages and
  masses from our simulated photometry using isochrones is
  demonstrated to be unreliable even for typical accretors. Although
  current brown dwarf disc candidate selection criteria have been
  shown to be largely reliable when applied to our model grid we
  suggest improved selection criteria in several colour indices. We
  show that as accretion rates increase brown dwarf disc systems are
  less likely to be correctly identified. This suggests that, within
  our grid, systems with higher accretion rates would be
  preferentially lost during brown dwarf target selection. We suggest
  that observations used to assert a $\dot{M}\propto M_*^2$
  relationship may contain an intrinsic selection bias.

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.ps}
  \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
    inclination, shown as top, middle and lower panels
    respectively. The magnitudes of systems with $M_*=0.04M_{\odot}$,
    an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
    days are shown as solid lines. The systems with accretion rates of
    \logmdot = $-$12, $-$9 and $-$7, are shown in black, red and blue
    respectively. The panels also show the systems with the highest
    accretion rate but for a rotation rate of 5 days, as a dashed
    line. The vertical dotted lines show the inclinations of
    71$^{\circ}$ and 56$^{\circ}$. Finally, the inset panel simply
    shows a magnification of the region of interested for the $M_J$
    magnitude. \label{flare_mag}}
\end{figure*}
